Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
general updates1

There are a number of different approaches to building physical quantum computing hardware being pursued by various research groups and companies,
each with their own advantages and disadvantages. Some of the types of experimentally implemented qubits include trapped ions, nitrogen-vacancy centres,
 quantum silicon photonics and superconducting, to name but a few. The qubits used to implement the both phase estimation algorithm and the variational
  quantum eigensolver were Xmon transmon qubits, a superconducting qubit built around a superconducting quantum interference device, or SQUID.
  A SQUID is made of a superconducting loops and Josephson junctions. The state of a qubit is determined by how many pairs of electrons tunnel
  across the Josephson junctions. Variations of the superconducting qubit are being developed by companies such as D-wave, IBM and Rigetti in the
  current race for quantum supremacy.

>>>>

There are a number of different approaches to building physical quantum computing hardware being pursued by various research groups and companies,
each with their own advantages and disadvantages. Some of the types of experimentally implemented qubits include trapped ions, nitrogen-vacancy centres,
 quantum silicon photonics and superconducting, to name but a few. The qubits used to implement both the phase estimation algorithm and the variational
  quantum eigensolver were Xmon transmon qubits, a superconducting qubit built around a superconducting quantum interference device, or SQUID.
  A SQUID is made of a superconducting loops and Josephson junctions. The state of a qubit is determined by how many pairs of electrons tunnel
  across the Josephson junctions. Variations of the superconducting qubit are being developed by companies such as D-wave, IBM and Rigetti in the
  current race for quantum supremacy.
